MCFA on Galah

### 2018-11-05 article/ms.tex
add figure

We sorted the elemental abundances by the number of stars
with reliable measurements, from highest to lowest. Starting
with Fe, we iterated over each element and counted the number
of stars with reliable measurements of that element and all
other elements earlier in the list. We illustrate this process
in Figure~\ref{fig:galah-abundance-flags}, where we show that
if we include the top 15 elemental abundances, we would have
\todo{X} stars with reliable measurements in all fifteen elements.
This is relevant to the approach we use here, as the method
described here requires no missing data.

@@

\subsubsection{Search strategy} \label{sec:experiment-galah-search}

>>>>

We sorted the elemental abundances by the number of stars
with reliable measurements, from highest to lowest. Starting
with Fe, we iterated over each element and counted the number
of stars with reliable measurements of that element and all
other elements earlier in the list. We illustrate this process
in Figure~\ref{fig:galah-abundances}, where we show that
if we include the top 15 elemental abundances, we would have
\todo{X} stars with reliable measurements in all fifteen elements.
This is relevant to the approach we use here, as the method
described here requires no missing data.

\begin{figure*}
	\includegraphics[width=1.0\textwidth]{experiments/galah-abundances.png}
    \caption{\todo{Caption}}
    \label{fig:galah-abundances}
\end{figure*}

@@

%\subsubsection{Search strategy} \label{sec:experiment-galah-search}

The expectation-maximization procedure outlined in Section \ref{sec:methods} describes 
the process of refining our estimate of the model parameters $\vec\psi$ until
the improvement in log probability between iterations decreases below some
pre-defined threshold. This method is valid for a pre-defined number of latent
factors, and a pre-defined number of components to cluster in latent space.
In practice these values are not known. For the purposes of this work, we 
perform a grid-based search in $J$ and $K$, perform E-M for each combination of
$J$ and $K$, and record the optimal parameters.

We trial the number of latent factors from $J = 1$ to $J = 10$, and trial the
number of clustering components from $K = 1$ to $K = 100$. We re-initialise the
mixture for each new trial of $\{J, K\}$, and do not make use of results from
`nearby' mixtures.

% Run this.
